---
title: "Graph Regression"
output: html_notebook
---

```{r Setup}
pacman::p_load(statnet,dplyr)
```

```{r Create Data}
KNOKI <-  matrix(
  c(0,1,0,0,1,0,1,0,1,0,1,0,1,1,1,0,1,1,1,0,0,1,0,1,1,1,1,0,0,1,1,1,0,0,1,0,1,0,0,0,1,1,1,1,0,0,1,1,1,1,0,0,1,0,0,0,1,0,1,0,0,1,0,1,1,0,0,0,0,0,1,1,0,1,1,0,1,0,1,0,0,1,0,0,1,0,1,0,0,0,1,1,1,0,1,0,1,0,0,0),
  nrow=10,
  ncol=10,
  byrow=T)
dimnames(KNOKI) = list(c(1,2,3,4,5,6,7,8,9,10), c("C","C","E","I","M","W","N","U","W","W"))

KNOKE <-  matrix(
  c(0,0,1,0,1,0,0,1,1,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,1,1,0,0,0,1,1,1,0,0,1,1,0,0,0,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,1,1,0,0,1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0),
  nrow=10,
  ncol=10,
  byrow=T)

dimnames(KNOKE) = list(c(1,2,3,4,5,6,7,8,9,10), c("C","C","E","I","M","W","N","U","W","W"))

KNOKI.n <- as.network(KNOKI)
KNOKE.n <- as.network(KNOKE)
```

```{r Have a look, paged.print=TRUE}
KNOKI.n
KNOKE.n
summary(KNOKI.n)
summary(KNOKE.n)
```

```{r Create Matrix representations}
# Remove diagonal because it throws off any matrix calculations
KNOKI.m <- diag.remove(as.sociomatrix(KNOKI.n)) 
KNOKE.m <- diag.remove(as.sociomatrix(KNOKE.n))

# Is density == mean for a network?
mean(KNOKI.m,na.rm = T) == network.density(KNOKI.n)
```

```{r Univariate descriptive statistics for Knoke information network rows}
mat <- t(data_frame(
mean = round(apply(KNOKI.m, 1, mean, na.rm = T),3),
stdev = round(apply(KNOKI.m, 1, sd, na.rm = T),3),
sum = round(apply(KNOKI.m, 1, sum, na.rm = T),3),
var = round(apply(KNOKI.m, 1, var, na.rm = T),3),
min = round(apply(KNOKI.m, 1, min, na.rm = T),3),
max = round(apply(KNOKI.m, 1, max, na.rm = T),3)
)) %>% data.frame()
colnames(mat) <- colnames(KNOKI.m)
mat
```

```{r Univariate descriptive statistics for Knoke information network columns}
mat <- t(data_frame(
mean = round(apply(KNOKI.m, 2, mean, na.rm = T),3),
stdev = round(apply(KNOKI.m, 2, sd, na.rm = T),3),
sum = round(apply(KNOKI.m, 2, sum, na.rm = T),3),
var = round(apply(KNOKI.m, 2, var, na.rm = T),3),
min = round(apply(KNOKI.m, 2, min, na.rm = T),3),
max = round(apply(KNOKI.m, 2, max, na.rm = T),3)
)) %>% data.frame()
colnames(mat) <- colnames(KNOKI.m)
mat
```

```{r Correlate networks}
gcor(list(KNOKE, KNOKI))
```


```{r QAP test}
(KNOK.cor <- qaptest(list(KNOKE, KNOKI), gcor, g1=1, g2=2, reps=2000))
```
`p(f(perm) >= f(d)): 0.7`  = Probability that the correlation beteen the two networks is smaller or equal to a random graph
`p(f(perm) <= f(d)): 0.434` = Probability that the correlation between the two networks is bigger than or equal to a random graph

In other words. 
  
  1. Correlate (Pearson) G1 and G2 ```gcor(list(KNOKE, KNOKI))```, which gives you  ```r (gcor(list(KNOKE, KNOKI)))[2]``` correlation.
  2. Generate random graphs G3:G2003 and correlate G1 with each.
  3. Out of the 2000 times, how many of them had a correlation of ```r (gcor(list(KNOKE, KNOKI)))[2]``` or higher?
  4. the answer is ```0.424*2000 = ``` ```r 0.424*2000```
  
Match the above to Figure 18.8 in the Hanneman chapter...

Some legwork guys...

```{r Nicer look at the model}
summary(KNOK.cor)
```
